---
title: "Eating Out"
author: "MarenaO"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```


According to the plot, I can conclude that out of white people, black people, and other people, the white people seem to be eating out the most.

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

According to the numerical results, I can conclude that white people were eating out more than the other races in this dataset. There were around 83% of white people eating out, compared to 69% from the black and 72% from the other races.

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```

According to the inferential data, I can conclude that there is a statistically significant difference between white and black, and white and other. This is due to their being a low p-value running the fisherXY test. Although, the fisherXY test concluded that there is no statistically significant difference between black and others, due to the p-value not being low.

The question to be answered was "which race eats out the most?" The plot for this dataset showed that the white people eat out the most compared to black and other races. I can conclude this because the bar for the white people was higher than the bar for the black and other people. Running the numerical results, I can conclude that I can conclude that white people were eating out more than the other races in this dataset, with around 83% of white people eating out. I then ran a fisher test and fisherXY test to confirm my numerical results. The inferential results showed that there was a statistical significance between white and black, and white and other, since the result gave a low p-value. Although, the inferential results showed that there was no statistically significant difference between black and others.